\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand*{\Lsquare}{
	\tikz[baseline]{
		\fill (-0.25ex,0.40ex) rectangle (0.25ex,0.90ex);
		\draw (0,0.65ex) -- (-1.0ex,0.65ex);
		\draw (-1.0ex,0.65ex) -- (-1.0ex,2.60ex);
	}
}

\newcommand*{\Ldotdash}{
	\tikz[baseline]{
		\draw[white] (0,0.5ex) -- (-1ex,0.5ex);
		\fill (0,0.5ex) circle (0.25ex);
		\draw (0,0.5ex) -- (0,0.60);
		\draw[densely dashed] (0,0.5ex) -- (3.0ex,0.5ex);
	}
}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Marco A Lopez} \\ \vspace{1pt}
    \small 214-621-5290 $|$ \href{mailto:x@x.com}{\underline{marcoalopez0730@gmail.com}} $|$ 
    \href{https://linkedin.com/in/marco-lopez-67a264149/}{\underline{linkedin.com/in/marco-lopez-67a264149/}} $|$
\href{https://github.com/Gale748}{\underline{github.com/Gale748}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Tarrant County College, Southeast Campus}{August 2020 -- May 2023}
      {Associate of Science in Engineering}{Arlington, TX}
    \resumeSubheading
      {Texas Christian University}{August 2017 -- May 2019}
      {B.S Mechanical Engineering}{Fort Worth, TX}
  \resumeSubHeadingListEnd
  
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, JavaScript, HTML/CSS, \LaTeX, Bash, zsh} \\
     \textbf{Developer Tools}{: Git, Docker, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}\\
     \textbf{CAD Software}{: PTC Creo, Fusion 360}\\
     \textbf{3D Printing}{: SLA, SLS}\\
     \textbf{Spoken Languages}{: English, Spanish }\\
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Library Service Representative}{August 2021 -- Present}
      {Grand Prairie Memorial Library}{Grand Prairie, TX}
      \resumeItemListStart
        \resumeItem{Assisted patrons with various computer-related inquiries, including troubleshooting, software usage, and device configuration.}
        \resumeItem{Provided guidance and support for completing forms, documents, and printing services.}
        \resumeItem{Collaborated with a team of librarians and staff to ensure efficient operations and a welcoming environment for library patrons.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Bakery Clerk}{March 2020 -- December 2020}
      {Whole Foods Market}{Dallas, TX}
      \resumeItemListStart
        \resumeItem{Prepared and baked a variety of artisan bread, pastries, cakes, and other baked goods according to established recipes and standards.}
        \resumeItem{Maintained a clean and organized work area, following food safety and sanitation guidelines.}
        \resumeItem{Provided exceptional customer service, offering product recommendations and answering inquiries about ingredients, flavors, and allergens.}
    \resumeItemListEnd

    \resumeSubheading
      {Customer Service Representative}{August 2017 -- August 2019}
      {The Home Depot}{Grand Prairie, TX}
      \resumeItemListStart
        \resumeItem{Assisted customers in finding products, answering questions, and providing information on product features, specifications, and usage.}
        \resumeItem{Processed customer orders accurately and efficiently, ensuring timely delivery or pickup.
Resolved customer complaints and concerns in a professional and courteous manner, utilizing effective problem-solving skills to achieve customer satisfaction.}
        \resumeItem{Utilized computer systems and software applications to access product information, check inventory availability, and place orders.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    \resumeProjectHeading
          {\textbf{Simple Locking Mechanism} $|$ \emph{PTC Creo}}{January 2023 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a locking mechanism using PTC Creo, a powerful computer-aided design (CAD) software, to enhance the security and functionality of a mechanical device. Leveraging the capabilities of PTC Creo, the project involved designing, modeling, and simulating a simple yet effective locking mechanism that could be implemented in various applications.}
            % \resumeItem{Utilized PTC Creo's intuitive interface and robust design tools to create a 3D model of the locking mechanism.}
            % \resumeItem{Documented the design process, including sketches, drawings, and annotations.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Encrypto} $|$ \emph{Python}}{July 2022 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a Discord bot capable of encrypting and decrypting messages on user command, enhancing communication privacy and security within the platform. Leveraged Python and the Discord API to create a versatile and user-friendly bot that offered end-to-end encryption for sensitive conversations.}
            % \resumeItem{Implemented encryption algorithms, such as AES or RSA, to ensure secure message transmission and storage.}
            % \resumeItem{Conducted rigorous testing and debugging to identify and resolve potential vulnerabilities or issues related to encryption and decryption procedures.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

 %-----------REFERENCES-----------
\section{References}
\resumeSubHeadingListStart
\resumeSubheading
{Alejandro Oranday}
{\href{mailto:alejandro@oran.day}{\underline{alejandro@oran.day}}}
{Physics PhD Candidate at Indiana University}{}
\resumeSubheading
{Evan Shrestha}
{\href{mailto:evanshrestha@gmail.com}{\underline{evanshrestha@gmail.com}}}
{Machine Learning Engineer at Discord}{}
\resumeSubheading
{Mathew Puente}
{\href{mailto:evanshrestha@gmail.com}{\underline{mathewjpuente@gmail.com}}}
{Software Engineer at Lockheed Martin}{}
\resumeSubHeadingListEnd
%-------------------------------------------
\end{document}